MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-04-02 MAESTROeX_I/intro.tex
reordered references

In recent years, a number of alternative approaches to modelling low Mach number flows have been developed. These include semi-implicit all-Mach number solvers, where the Euler equations
are split into an acoustic part and an advective part \citep{Degond2009,Cordier2012,Haack2012,Chalons2016,Kwatra2009,Happenhofer2013,Padioleau2019}. The fast acoustic waves are then
solved using implicit time integration, while the slow material waves are solved explicitly. Another approach is to use preconditioned all-Mach number solvers
\citep{Miczek2014,Barsukow2016}, where the numerical flux is multiplied by a preconditioning matrix. This reduces the stiffness of the system at low Mach numbers, while retaining the
correct scaling behavior. In the reduced speed of sound technique (RSST) and related methods, the speed of sound is artificially reduced by including a suitable scaling factor in the
continuity equation, reducing the restriction on the size of the timestep \citep{Rempel2005,Hotta2012,Wang2015,Takeyama2017,Iijima2018}. The MUSIC code uses fully implicit time integration for the compressible Euler equations, which therefore allows for arbitrarily large timesteps \citep{Viallet2011,Viallet2015,Goffrey2016}.

>>>>

In recent years, a number of alternative approaches to modelling low Mach number flows have been developed. These include semi-implicit all-Mach number solvers, where the Euler equations
are split into an acoustic part and an advective part \citep{Kwatra2009,Degond2009,Cordier2012,Haack2012,Happenhofer2013,Chalons2016,Padioleau2019}. The fast acoustic waves are then
solved using implicit time integration, while the slow material waves are solved explicitly. Another approach is to use preconditioned all-Mach number solvers
\citep{Miczek2014,Barsukow2016}, where the numerical flux is multiplied by a preconditioning matrix. This reduces the stiffness of the system at low Mach numbers, while retaining the
correct scaling behavior. In the reduced speed of sound technique (RSST) and related methods, the speed of sound is artificially reduced by including a suitable scaling factor in the
continuity equation, reducing the restriction on the size of the timestep \citep{Rempel2005,Hotta2012,Wang2015,Takeyama2017,Iijima2018}. The MUSIC code uses fully implicit time integration for the compressible Euler equations, which therefore allows for arbitrarily large timesteps \citep{Viallet2011,Viallet2015,Goffrey2016}.
